Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
finish g=0 proof (mostly)

Now we can induct on cases (a)-(e) of \ref{lem:g_0_admissible_cases}
to obtain bounds on the minimal generator and relation degrees for
canonical rings of curves in the genus 0 case.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. Since
this case satisfies all of the conditions by Lemma \todo{need this case
to satisfy conditions for adding points}, the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ is generated up to degree $e := \max(5, e_1',
\ldots, e_r')$ with relations generated up to degree $2e$.
Furthermore, Lemma ~\ref{lem:sat_three_induction}(d)
implies that these cases satisfy all of the hypotheses of Theorem
~\ref{thm:ram_order_ind}.

So if $r > 5$, then $\sigma$ ``lies above'' the case $\sigma', J$
where $\sigma'$ has $r$ many ramification points all of order $3$
and $J = \{1, \ldots, r\}$. If $r \leq 5$, then $\sigma$ ``lies
above'' one of the base cases of Lemma ~\ref{lem:g_0_admissible_cases}.
In either case, there is a $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$ satisfying the property that for all $i \in J$,
$e_i \geq e_i'$ and $e_i = e_i'$ otherwise where $(\sigma', J)$
is either a base case from Lemma ~\ref{lem:g_0_admissible_cases}
or the case from $r > 5$.

>>>>

Now we can induct on cases (a)-(k) of \ref{lem:g_0_admissible_cases}
to obtain bounds on the minimal generator and relation degrees for
canonical rings of curves in the genus 0 case.

@@

If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. This case
clearly satisfies the conditions of Lemma
~\ref{lem:sat_three_induction} (recall from Subsection ~\ref
{ssec:g_0_saturation} that saturation is 3 here), and the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ for any $r > 5$ is generated up to
degree $e := \max(5, e_1', \ldots, e_r')$ with relations generated
up to degree $2e$. Furthermore, Lemma ~\ref{lem:n-3s-admissible}
implies that these cases satisfy all of the conditions of Theorem
~\ref{thm:ram_order_ind}.

So if $r > 5$, then $\sigma$ ``lies above'' the case $(\sigma', J)$
where $\sigma'$ has $r$ many ramification points all of order $3$
and $J = \{1, \ldots, r\}$ and these underlying cases satisfy
all of the hypotheses of Theorem ~\ref{thm:ram_order_ind}.
If $r \leq 5$, then $\sigma$ ``lies above'' one of the base cases
of Lemma ~\ref{lem:g_0_admissible_cases}, all of which satisfy
the hypotheses of Theorem ~\ref{thm:ram_order_ind} as well.

So for any $r > 0$, there is a $(\sigma', J)$, either from
Lemma ~\ref{lem:g_0_admissible_cases} or corresponding to
the $r > 5$ case with ramification orders all $3$, with $\sigma' =
(0; e_1', \ldots, e_r'; 0)$ satisfying the property that for all $i
\in J$, $e_i \geq e_i'$ and $e_i = e_i'$ otherwise.
